Review of Assigned Readings

### 2018-01-04 paper/paper.tex
added § with research results in the abstract

%************************** Abstract ************************** 
\begin{abstract}
\pagenumbering{Roman}
This paper, examines the dynamics between the amount of twitter activity regarding bitcoin and the actual price fluctuation of bitcoin. For the analysis two sets of data have been collected. One reflecting twitter activity and the other one showing the bitcoin prices for the same period. Based on that an econometric model is used for the statistical analysis and the interpretation of the results.\\

***INPUT ALEN @DIMI: ADD JUST KEY FINDING THE REST I LIKE***\\

This work was created in the context of a programming course for economists at the university of St. Gallen. To not exceed the framework of this study we require extensive knowledge in econometrics and take concepts as known. The underlying goal was to get familiar with software engineering tools and project management. Therefore, the academic content of this work is neither completed nor concluding.\\
\end{abstract}

>>>>

%************************** Abstract ************************** 
\begin{abstract}
\pagenumbering{Roman}
This paper, examines the dynamics between the amount of twitter activity regarding bitcoin and the actual price fluctuation of bitcoin. For the analysis two sets of data have been collected. One reflecting twitter activity and the other one showing the bitcoin prices for the same period. Based on that an econometric model is used for the statistical analysis and the interpretation of the results.\\
The evaluation of the model showed that changes in twitter activity on bitcoin have a minimal and insignificant effect on the future price development of bitcoin. Accordingly, aggregate twitter fees are not a good source to predict changes in bitcoin prices. This result must be understood with caution, because it only applies for the specific time interval of our observations, which is about 8 days and not for the past or future trend of cryptocurrencies. \\
This work was created in the context of a programming course for economists at the university of St. Gallen. To not exceed the framework of this study we require extensive knowledge in econometrics and take concepts as known. The underlying goal was to get familiar with software engineering tools and project management. Therefore, the academic content of this work is neither completed nor concluding.\\
\end{abstract}
